Cleaning Data

### 2021-07-19 cleaning_aid.Rmd
First changes
codes for gene set library

x <- read.table("PMC 2019 - analysis.tsv",header=TRUE,fill=TRUE,sep="\t")
head(x)
colnames(x)

@@

>>>>

x <- read.table("PMC 2019 - analysis.tsv",header=TRUE,fill=TRUE,sep="\t")
head(x)
colnames(x)
dim(x)

@@

# Gene set library
GSL <-x$Gene.set.library
GSL_split <- strsplit(GSL,", ")
GSL <- unlist(GSL_split)
table(GSL)
